[Artifact Presentation] Damegender: \\ Writing and Comparing Gender Detection Tools

### 2020-05-15 paper2sattose.tex
Included some comments just in case David has a look at them

@@

In Table~\ref{table:ApisAndErrors} we can observe a high index of errors in \texttt{Nameapi} and \texttt~Namsor} and a low index of errors in \texttt{GenderApi} and \texttt{damegender}.

>>>>

\grex{Deberiamos explicar que es cada una de las metricas. Y tambien por que tenemos 1.0 de recall en todos los casos.}

@@

In Table~\ref{table:ApisAndErrors} we can observe a high index of errors in \texttt{Nameapi} and \texttt{Namsor} and a low index of errors in \texttt{GenderApi} and \texttt{damegender}.

\grex{Aqui haria falta indicar por que hacemos esta comparacion y que queremos aprender de ella}
